### 2019-01-02 abstract.tex
Reviewer #1 comment implemented addressing Issue #32
Reviewer 2 minor comments mostly resolved #39

Today, climate change drives humanity's search for new ways to generate 
carbon-free, reliable base-load power. Thus,
interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
with multiple new companies pursuing commercialization of \gls{MSR} 
designs (e.g. Transatomic, Terrapower, Terrestrial, Moltex Energy, Thorcon). To further 
develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 
fueled \gls{MSR} depletion and fuel processing. However, most 
contemporary nuclear reactor physics software is unable to perform high-fidelity 
full-core depletion calculations for a reactor design with online reprocessing. This paper 
introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
SERPENT2, to simulate \gls{MSR} online reprocessing by modeling the changing 
isotopic composition of \gls{MSR} fuel salt. This work demonstrates SaltProc capabilities
for a full-core, high-fidelity model of the commercial \gls{MSBR} 
concept and verifies these results to results in the literature from 
independent, lower-fidelity analyses.

>>>>

Today, climate change drives humanity's search for new ways to generate 
carbon-free, reliable base-load power. Thus,
interest in advanced nuclear energy and particularly \glspl{MSR} has resurged, 
with multiple new companies pursuing commercialization of \gls{MSR} 
designs. To further 
develop these \gls{MSR} concepts, researchers need simulation tools for analyzing liquid 
fueled \gls{MSR} depletion and fuel processing. However, most 
contemporary nuclear reactor physics software is unable to perform high-fidelity 
full-core depletion calculations for a reactor design with online reprocessing. This paper 
introduces a Python package, SaltProc, which couples with the Monte Carlo code, 
SERPENT2, to simulate \gls{MSR} online reprocessing by modeling the changing 
isotopic composition of \gls{MSR} fuel salt. This work demonstrates SaltProc capabilities
for a full-core, high-fidelity model of the commercial \gls{MSBR} 
concept and verifies these results to results in the literature from 
independent, lower-fidelity analyses.

### 2019-01-02 introduction.tex
Reviewer 2 minor comments mostly resolved #39

\begin{table}[ht!]
\caption{Tools and methods for \glspl{MSR} fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ m | b | x } 
\hline Neutronic code    & \qquad Authors & Spectrum   \\
\hline
\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez 
\emph{et al.}, 2014; Heuer \emph{et al.}, 2014  
\cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 
\cite{fiorina_investigation_2013}            & fast \\
\hline
KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu 
\emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
SERPENT 2 \cite{leppanen_serpent_2015}  & Aufiero \emph{et al.}, 2013 
\cite{aufiero_extended_2013} & fast \\
\hline
DIF3D \cite{derstine_dif3d:_1984} & Zhou \emph{et al.}, 2018 
\cite{zhou_fuel_2018} & fast \\
\hline
MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 
2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; 
Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& 
thermal\\
\hline
SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 
2014; Betzler \emph{et al.}, 2017 
\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal/ fast\\
\hline
SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & 
thermal\\
\hline
\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ 
\hline
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core continuously or at specific time steps 
(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
time and restarts with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing and refill using a single 
or multiple unit cell. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
as well as the current work also employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. Aufiero \emph{et al.} explicitly
introduced online fuel reprocessing in the system of equations by adding effective 
decay and transmutation terms for the different nuclides. The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}. In his work SERPENT was 
used for solution of the matrix exponential derived from the system of the Bateman 
equations \cite{aufiero_extended_2013}. Similar approach is adopted to model true 
continuous feeds and removals using MCNP transport code listed in references 
\cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.

>>>>

\begin{table}[ht!]
\caption{Tools and methods for \glspl{MSR} fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ m | b | x } 
\hline Neutronic code    & \qquad Authors & Spectrum   \\
\hline
\gls{MCNP}/REM \cite{noauthor_mcnp_2004,heuer_simulation_2010}  & Doligez 
\emph{et al.}, 2014; Heuer \emph{et al.}, 2014  
\cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
ERANOS \cite{ruggieri_eranos_2006}  & Fiorina \emph{et al.}, 2013 
\cite{fiorina_investigation_2013}            & fast \\
\hline
KENO-IV/ORIGEN \cite{goluoglu_monte_2011,gauld_isotopic_2011}     & Sheu 
\emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
SERPENT 2 \cite{leppanen_serpent_2015}  & Aufiero \emph{et al.}, 2013 
\cite{aufiero_extended_2013} & fast \\
\hline
DIF3D \cite{derstine_dif3d:_1984} & Zhou \emph{et al.}, 2018 
\cite{zhou_fuel_2018} & thermal/ fast \\
\hline
MCODE/ORIGEN2 \cite{xu_mcode_2008,croff_users_1980}      & Ahmad \emph{et al.}, 
2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
\gls{MCNP}6/CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; 
Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& 
thermal\\
\hline
SCALE/TRITON \cite{bowman_scale_2011,powers_new_2013}    & Powers \emph{et al.}, 
2014; Betzler \emph{et al.}, 2017 
\cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal/ fast\\
\hline
SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & 
thermal\\
\hline
\gls{MCNP}/REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ 
\hline
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

Many liquid-fueled \gls{MSR} designs rely on online fuel processing in which  
material moves to and from the core continuously or at specific time steps 
(batch-wise). In the batch-wise approach, the burn-up simulation stops at a given 
time and restarts with a new liquid fuel composition (after removal of discarded 
materials and addition of fissile/fertile materials). \gls{ORNL} researchers 
have developed ChemTriton, a Python-based script for SCALE/TRITON which uses the 
batch-wise approach to simulate a continuous reprocessing and refill using a single 
or multiple unit cell. ChemTriton models salt 
treatment, separations, discharge, and refill using a unit-cell \gls{MSR} 
SCALE/TRITON depletion simulation over small time steps to simulate continuous 
reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in 
references \cite{zhou_fuel_2018,sheu_depletion_2013,park_whole_2015, 
jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} 
as well as the current work also employ a batch-wise approach.

Accounting for continuous removal or addition presents a greater challenge since it 
requires adding a term to the Bateman equations. Fiorina \emph{et al.} simulated 
\gls{MSFR} depletion with continuous fuel salt reprocessing via introducing 
``reprocessing'' time constants into ERANOS transport code \cite{fiorina_investigation_2013}. Aufiero \emph{et al.} improved SERPENT2 using similar methodology by explicitly introducing 
continuous reprocessing in the system of Bateman equations by adding effective decay and transmutation terms for the different nuclides \cite{aufiero_extended_2013}.

The latest SCALE release will also have the same functionality using truly continuous removals \cite{betzler_implementation_2017}. In his work SERPENT was 
used for solution of the matrix exponential derived from the system of the Bateman 
equations \cite{aufiero_extended_2013}. Similar approach is adopted to model true 
continuous feeds and removals using MCNP transport code listed in references 
\cite{doligez_coupled_2014,heuer_towards_2014,nuttin_potential_2005}.

### 2019-01-02 results.tex
Reviewer 2 minor comments mostly resolved #39

Additionally, the presence of rubidium, strontium, cesium, and barium in the 
core are disadvantageous to reactor physics. In fact, SaltProc fully removes all these elements every 3435 days (not a small mass fraction every 3 days) 
which causes the multiplication factor to jump by approximately 450 
pcm, and limits using the batch approach for online reprocessing simulations. 
In future versions of SaltProc this drawback will be eliminated by removing 
elements with longer cycle times (seminoble metals, volatile fluorides, Rb, Sr,
 Cs, Ba, Eu) using different approach. Only mass fraction (calculated 
 separately for each reprocessing group) will be removed every depletion step 
 (e.g. 3 days) instead of removing 100\% of element atoms after cycle time.
Overall, the effective multiplication factor gradually decreases from 1.075 to 
$\approx$1.02 at equilibrium after approximately 6 years of irradiation.

>>>>

Additionally, the presence of rubidium, strontium, cesium, and barium in the 
core are disadvantageous to reactor physics. In fact, SaltProc fully removes all these elements every 3435 days (not a small mass fraction every 3 days) 
which causes the multiplication factor to jump by approximately 450 
pcm, and limits using the batch approach for online reprocessing simulations. 
In future versions of SaltProc this drawback will be eliminated by removing 
elements with longer residence times (seminoble metals, volatile fluorides, Rb, Sr,
 Cs, Ba, Eu) using different approach. Only mass fraction (calculated 
 separately for each reprocessing group) will be removed every depletion step 
 (e.g. 3 days) instead of removing 100\% of element atoms after cycle time.
Overall, the effective multiplication factor gradually decreases from 1.075 to 
$\approx$1.02 at equilibrium after approximately 6 years of irradiation.
